1 Report ASP20 Boost

### 2020-06-05 Reports/sample_report/1_REPORT.tex

\usepackage{graphicx}

@@

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{1 Report ASP20 Boost}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{First Report}
\author{Johannes Strauß \and Levin Wiebelt \and Sebastian Aristizabal}
\date{03 June 2020}

@@

In the \texttt{report} folder there's two \texttt{.bib} files. These
contain all reference we should need. To update the \texttt{package.bib}
write the name of the package in the following chunk and \emph{actively}
run it (It should be installed in your terminal). The\texttt{citavi.bib}
file needs to be exported from citavi.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# automatically create a bib database for R packages}
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{write\_bib}\NormalTok{(}\KeywordTok{c}\NormalTok{(}
  \KeywordTok{.packages}\NormalTok{(), }\StringTok{\textquotesingle{}R6\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}knitr\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}rmarkdown\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}asp20model\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}gamboostLSS\textquotesingle{}}\NormalTok{,}\StringTok{\textquotesingle{}mboost\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}tidyverse\textquotesingle{}}  
\NormalTok{), }\StringTok{\textquotesingle{}packages.bib\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

JS: During the learning process, we tried several methods to implement
the required functionality. At first, we started with a simple function
in a R-File. While looking at other online resources, we agreed on using
the asp20model packages as a requirement for our package and inheriting
the existing LocationScaleRegression class. Our
\texttt{LocationScaleRegressionBoost} R6 class implements a boosting
algorithm, two functions within the model for calculating the best
fitting covariate with respect to Gamma and Beta and has four new
variables which are set at the initialization of the model to reduce
computation time of the Projection Matrixes during the gradient boosting
(subject to change). The package provides the gradient boost function
for the \texttt{LocationScaleRegressionBoost} class, which uses the two
model functions to optimize stepwise the Beta and Gamma Vector.

@@

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-R-R6}{}%
Chang, Winston. 2019. \emph{R6: Encapsulated Classes with Reference
Semantics}. \url{https://CRAN.R-project.org/package=R6}.

@@

\leavevmode\hypertarget{ref-R-asp20model}{}%
Riebl, Hannes. 2020. \emph{Asp20model: An R6 Class for Location-Scale
Regression Models}.
\end{cslreferences}

>>>>

\usepackage{graphicx,grffile}

@@

\title{1 Report ASP20 Boost}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{First Report}
\author{Johannes Strauß \and Levin Wiebelt \and Sebastian Aristizabal}
\date{05 Juni 2020}

@@

In the \texttt{report} folder there's two \texttt{.bib} files. These
contain all reference we should need. To update the \texttt{package.bib}
write the name of the package in the following chunk and \emph{actively}
run it (It should be installed in your terminal). The\texttt{citavi.bib}
file needs to be exported from \texttt{citavi}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# automatically create a bib database for R packages}
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{write_bib}\NormalTok{(}\KeywordTok{c}\NormalTok{(}
  \KeywordTok{.packages}\NormalTok{(), }\StringTok{'R6'}\NormalTok{, }\StringTok{'knitr'}\NormalTok{, }\StringTok{'rmarkdown'}\NormalTok{, }\StringTok{'asp20model'}\NormalTok{, }\StringTok{'gamboostLSS'}\NormalTok{,}\StringTok{'mboost'}\NormalTok{, }\StringTok{'tidyverse'}  
\NormalTok{), }\StringTok{'packages.bib'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

JS: During the learning process, we tried several methods to implement
the required functionality. At first, we started with a simple function
in a R-File. While looking at other online resources, we agreed on using
the asp20model packages as a requirement for our package and inheriting
the existing LocationScaleRegression class. Our
\texttt{LocationScaleRegressionBoost} R6 class implements a boosting
algorithm, two active fields within the model for calculating the best
fitting covariate with respect to Gamma and Beta and has four new
variables which are set at the initialization of the model to reduce
computation time of the Projection Matrixes during the gradient boosting
(subject to change). The package provides the gradient boost function
for the \texttt{LocationScaleRegressionBoost} class, which uses the two
model functions to optimize stepwise the Beta and Gamma Vector.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-R6}{}%
Chang, Winston. 2019. \emph{R6: Encapsulated Classes with Reference
Semantics}. \url{https://CRAN.R-project.org/package=R6}.

@@

\leavevmode\hypertarget{ref-R-asp20model}{}%
Riebl, Hannes. 2020. \emph{Asp20model: An R6 Class for Location-Scale
Regression Models}.
